---
title: "Homework10ExtraCredit"
author: "Barbara Bruno"
date: "2022-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#package(readr)
---
library(readr)
library(here)
library(tidyverse)
install.packages("rmarkdown")
install.packages("knitr")
library(rmarkdown)
library(knitr)


#git config --global user.email "bruno3@arizona.edu"

Read in the datafile
---
data01 <- read.csv("data/data/inflammation-01.csv", header = FALSE, sep = ',')

class(data01)


8B Dimensions 8B
----
dim(data01)



8C Particular columns
---
data01[c(1:4), c(1:10)]
data01[c(5:10), c(1:10)]


8D Addressing Columns By Name
---
#first row, all of the columns
patient_1 <- data01[1, ]

# max inflammation for patient 1
max(patient_1)

#Value if you want to change max to sum
# first row, all of the columns
patient_1 <- data01[1, ]

# max inflammation for patient 1
sum(patient_1)


8E Performing Statistics on the Data
---

#max inflammation for patient 2 day 7
min(data01[2,7])

8F Forcing R to Read Data as Numeric
---
mean(as.numeric(data01[1, ]))

8G Operations Across Margins of the Dataframe
---
avg_patient_inflammation <- apply(data01, 1, mean)
avg_day_inflammation <- apply(data01, 2, mean)

Step 9 Plotting the data
---
plot(avg_day_inflammation)

Question six : looking at two other statistics: the maximum and minimum inflammation per day.
---
max_day_inflammation <- apply(data01, 2, max)
plot(max_day_inflammation)

Question seven
---
min_day_inflammation <- apply(data01, 2, min)
plot(min_day_inflammation)

```{r}
plot(max_day_inflammation)
```




