---
title: "Homework10ExtraCredit"
author: "Barbara Bruno"
date: "2022-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#package(readr)
library(readr)
library(here)
library(tidyverse)
install.packages("rmarkdown")
install.packages("knitr")
library(rmarkdown)
library(knitr)

library(rmarkdown)
render("Homework10RMarkDownExtra.Rmd")

#git config --global user.email "bruno3@arizona.edu"

# read in the datafile
data01 <- read.csv("data/data/inflammation-01.csv", header = FALSE, sep = ',')

class(data01)

#Dimensions 8B
dim(data01)

<<<<<<< HEAD
##patient_inflammation <- read_csv(file = r_novice_inflammation_data)

#patient-inflammation <- read_csv(file = r-novice-inflammation-data,
# row_names=c("pat")
# show_row_types = FALSE)

#Particular columns 8C
data01[c(1:4), c(1:10)]

data01[c(5:10), c(1:10)]

---
8D. Addressing Columns By Name
---

# first row, all of the columns
patient_1 <- data01[1, ]

# max inflammation for patient 1
max(patient_1)

---
Value if you want to change max to sum
---

# first row, all of the columns
patient_1 <- data01[1, ]

# max inflammation for patient 1
sum(patient_1)

---
8E Performing Statistics On The Data
---

# max inflammation for patient 2 day 7
min(data01[2,7])

---
8F. Forcing R to Read Data as Numeric
---

mean(as.numeric(data01[1, ]))

---
8G. Operations across margins of the dataframe
---

avg_patient_inflammation <- apply(data01, 1, mean)
avg_day_inflammation <- apply(data01, 2, mean)

---
Step 9. Plotting the data
---

plot(avg_day_inflammation)

```{r, echo=FALSE}
plot(avg_day_inflammation)
```

---
Question 6: looking at two other statistics: the maximum and minimum inflammation per day.
---

max_day_inflammation <- apply(data01, 2, max)
plot(max_day_inflammation)

```{r, echo=FALSE}
plot(max_day_inflammation)
```

---
Question 7
---

min_day_inflammation <- apply(data01, 2, min)
plot(min_day_inflammation)

```{r, echo=FALSE}
plot(min_day_inflammation)
```





